---
title: "Standard Analytics Report"
format:
  docx:
    toc: true
    number-sections: true
date: "`r format(Sys.Date(), '%B %d, %Y')`"
params:
  ref_dates: NULL
  workforce_indicators: NULL
  wagebill_indicators: NULL
  plots: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 4.5
)

# draws one cached figure, or a placeholder when the panel has no data
show_plot <- function(name) {
  plot <- params$plots[[name]]
  if (is.null(plot)) {
    knitr::asis_output("*No data available for this indicator.*")
  } else {
    plot
  }
}

show_table <- function(x) {
  knitr::kable(x, digits = 2, format.args = list(big.mark = ","))
}
```

This report covers the period **`r params$ref_dates[1]`** to **`r params$ref_dates[2]`**. Every figure is drawn from the same pre-computed summaries the Standard Analytics dashboard serves, at the default grouping over reference dates.

# Key indicators

## Workforce

```{r}
show_table(params$workforce_indicators)
```

## Wage bill

```{r}
show_table(params$wagebill_indicators)
```

# Workforce

## Headcount over time

```{r}
show_plot("workforce_overview")
```

## Hiring

```{r}
show_plot("workforce_movement")
```

## Transitions between groups

```{r}
show_plot("workforce_transition")
```

## Retirement

```{r}
show_plot("workforce_retirement")
```

Projected retirements:

```{r}
show_plot("workforce_retirement_expected")
```

# Wage bill

## Wage bill over time

```{r}
show_plot("wagebill_overview")
```

## Wage distribution

```{r}
show_plot("wagebill_density")
```

Mean wage by decile:

```{r}
show_plot("wagebill_decile")
```

Compression ratio between the 10th and 90th percentile:

```{r}
show_plot("wagebill_compression")
```

## Labor movement costs

```{r}
show_plot("wagebill_movement")
```

## Retirement costs

```{r}
show_plot("wagebill_retirement")
```

Projected retirement costs:

```{r}
show_plot("wagebill_retirement_expected")
```

---

*Report generated on `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`.*
