---
title: "Workforce Analytics Report"
format: 
  docx:
    reference-doc: custom-reference.docx
    toc: true
    number-sections: true
    highlight-style: github
date: "`r format(Sys.Date(), '%B %d, %Y')`"
params:
  date_range: NULL
  workforce_group: NULL
  plot1: NULL
  plot2: NULL
  plot3: NULL
  plot4: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(dplyr)
thematic::thematic_rmd()
```

## Executive Summary

This report presents workforce headcount analytics for the selected time period (`r params$date_range[1]` to `r params$date_range[2]`). The analysis examines workforce composition, growth patterns, and personnel movements.

**Analysis Parameters:**

- **Time Frame:** `r params$date_range[1]` - `r params$date_range[2]`
- **Grouping Variable:** `r params$workforce_group`

---

## Headcount Trends

The following chart shows the evolution of headcount over time.

```{r plot1, fig.width=8, fig.height=5}
if (!is.null(params$plot1)) {
  params$plot1
}
```

**Key Observations:**

- Overall workforce size trajectory
- Growth or contraction periods
- Stability or volatility in headcount

---

## Total Headcount by Group

This section presents the total headcount broken down by the selected grouping variable.

```{r plot2, fig.width=8, fig.height=6}
if (!is.null(params$plot2)) {
  params$plot2
}
```

**Analysis:**

- Largest workforce segments
- Distribution across categories
- Workforce composition insights

---

## Growth Rate by Group

Year-over-year growth rates reveal which groups are expanding or contracting.

```{r plot3, fig.width=8, fig.height=6}
if (!is.null(params$plot3)) {
  params$plot3
}
```

**Insights:**

- Groups with highest growth rates
- Groups experiencing decline
- Overall workforce dynamics

---

## Personnel Movements

This analysis examines hires and separations over time.

```{r plot4, fig.width=8, fig.height=6}
if (!is.null(params$plot4)) {
  params$plot4
}
```

**Movement Analysis:**

- Hiring and attrition trends
- Turnover patterns
- Workforce stability indicators

---

## Conclusions and Recommendations

Based on the analysis presented in this report:

1. **Summary of key findings**
2. **Notable trends or patterns**
3. **Areas requiring attention**
4. **Recommendations for action**

---

*Report generated on `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`*
